---
title: "The distribution of *Rhea americana*  based on site-occupancy modeling, expert knowledge, and observations from citizen-science projects"
author: "André Luís Luza, Arthur Rodrigues, Viviane Zulian, Gonçalo Ferraz"
date: "22/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Who are we? What are we doing?

We are a team of researchers from the Universidade Federal de Santa Maria (UFSM) and Universidade Federal do Rio Grande do Sul (UFRGS) interested in using citizen-science data to modeling the distribution of iconic and endangered species, like the vinaceous-breasted amazon (*Amazona vinacea*) and the greater rhea (*Rhea americana*). This is a project focused on greater rhea distribution. The project aims to estimate the distribution of this species in the municipalities of Rio Grande do Sul (RS), the southermost state of Brazil. We will estimate distribution based on three sources of evidence: 1) detection in citizen-science projects (e.g. e-bird, gbif), 2) expert knowledge, and 3) site-occupancy modeling based on the integration of data from different citizen-science projects.

## What do we want from you?

We already gather information from the first and third sources of evidence. Now, we need your help!! As an expert, we would like to kindly ask you to share your knowledge about the great Rhea distribution in RS. To help you while sharing your knowledge, we built two iterative maps where you can drawn polygons with the distribution you know: 1) map with the boundaries of the municipalities of RS, and 2) municipality boundaries + cover of natural grasslands. Please, respect the order of maps.



```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
