---
title: "Modeling the distribution of Greater Rhea *Rhea americana* in Rio Grande do Sul"
author: "André Luza, Arthur Rodrigues, Viviane Zulian, Gonçalo Ferraz"
date: "22/09/2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Who are we? What are we doing?

We are a team of researchers from Universidade Federal de Santa Maria (UFSM) and Universidade Federal do Rio Grande do Sul (UFRGS) interested in using citizen-science data to modeling the distribution of iconic and endangered species like the vinaceous-breasted amazon (*Amazona vinacea*) and the greater rhea (*Rhea americana*). This is a project focused on greater rhea. 
The project aims to estimate the distribution of this species in the municipalities of Rio Grande do Sul (RS), the southermost state of Brazil. We will estimate distribution based on three sources of evidence: 1) detection data from citizen-science projects (e.g. e-bird, gbif), 2) expert knowledge, and 3) site-occupancy modeling based on the integration of data from different citizen-science projects.

## What do we want from you?

We already get information from the first and third sources of evidence. Now, we need your help to gather data for the second source!! As an expert, we would like to kindly ask you to share your knowledge about the great Rhea distribution in RS. To help you to share your knowledge, we built two iterative maps where you can drawn one or more polygons bounding the localities where you detected and / or know that Rhea can be detected. The maps are: 1) map with the boundaries of the municipalities of RS, and 2) map of RS with the cover of natural grasslands (from Hofmann et al. 2015).


```{r eruptions, echo=FALSE}


## functions
source ("R/functions.R")
## packages
source ("R/packages.R")

## carregar o shapefile dos municipios do RS
mymun <- readOGR (dsn=here("data","shape_munRS"), layer= "43MUE250GC_SIR")

## funcao interna para desenhar os poligonos
pol.coords <- function(input.polig){
  
  pol.coords <- data.frame(x=numeric(),y=numeric())
  total <- length(input.polig$geometry$coordinates[[1]])
  long.pol <- numeric()
  lat.pol <- numeric()
  for (i in 1:total){
    long.pol <- input.polig$geometry$coordinates[[1]][[i]][[1]]
    lat.pol <- input.polig$geometry$coordinates[[1]][[i]][[2]]
    
    
    coords <- data.frame(x=long.pol,y=lat.pol)
    
    pol.coords <- rbind(pol.coords, coords)
    
  }
  
  pol.coords 
}

make.polygon <- function(df){
  
  # and then something like this
  sp <- SpatialPolygons(list(Polygons(list(Polygon(df)), 1)))
  sp
  
}

ui <- fluidPage(
  titlePanel("Desenhe um polígono"),
  
  sidebarLayout(
    sidebarPanel(
      helpText(h2("Instruções:"),
               br(),
               "Insira pontos no mapa para desenhar um polígono
               ligando os pontos onde você já detectou ", em("Rhea americana"), 
               ".", 
               br(),
               br(),
               "Você pode desenhar quantos polígonos forem necessários. Para
               finalizar um polígono, você deve clicar no ponto onde iniciou o polígono.
               Tome cuidado para que seu polígono não sobreponha um município
               onde você não registrou a espécie.", 
               "Para se localizar no mapa, você verá o nome do município ao passar
               o mouse sobre o mapa do RS. Esta função fica desativada enquanto você está 
               desenho o polígono, para que não atrapalhe na visualização.",
               br(),
               "Na parte superior e direita do mapa você verá duas camadas de mapa disponíveis:
               StreetMap e Satelite. Explore estas opções para se localizar melhor.",
               br(),
               "Ao final do processo de desenho do polígono e preencher seus dados, clique em 'Send mail'.
               Três arquivos com o nome 'arquivo_poligono_Rhea' serão salvos automaticamente. 
               Os formatos são '.shp', 'dbf', e 'shx'. Por favor, envie os três arquivos
               para o email luza.andre@gmail.com"),
               textInput("from", "From:", value="from@account.com"),
               textInput("to", "To:", value="luza.andre@gmail.com"),
               textInput("name", "Your name:", value=""),
               br (),
      actionButton("send", "Send mail")
    ),
    mainPanel(
      leafletOutput("map")
    )
  )
)


server <- function(input, output, session){
  values <- reactiveValues()
  
  output$map <- renderLeaflet({
    
    leaflet(data=mymun) %>% 
      setView(lng = -52.8, lat = -30.5, zoom = 6) %>%
      # Add two tiles
      addTiles(options = providerTileOptions(noWrap = TRUE),group="StreetMap")%>%
      addProviderTiles("Esri.WorldImagery", group="Satelite")  %>%
      addDrawToolbar(
        targetGroup='Markers',
        polylineOptions = F,
        polygonOptions = T, 
        circleOptions = F,
        rectangleOptions = F,
        markerOptions = F,
        circleMarkerOptions = F,
        editOptions = editToolbarOptions(selectedPathOptions = selectedPathOptions())) %>%
      addLayersControl( baseGroups = c("StreetMap","Satelite"),
                        options = layersControlOptions(collapsed = TRUE)) %>%
      
      addPolygons(fillColor="white"
                  , fillOpacity = 0.1
                  , color= "white"
                  , stroke= FALSE
                  , highlight=highlightOptions(weight=0.5
                                               , color="gray"
                                               , fillOpacity= 0.3
                                               , fillColor="white"
                                               , bringToFront = FALSE)
                  , label = ~ NM_MUNICIP)
    
  })
  
  ## observe passar o mouse sobre os polygonos
  observe ({
    click <- input$map_shape_click 
    if (is.null (click))
      return ()
    else 
      leafletProxy ("map") %>%
      setView (lng=click$lng, lat= click$lat, zoom = 6)
  })
  
  # observar o clique e usar a funcao definida fora para desenhar o poligono
  observeEvent(input$map_draw_all_features, {
    
    values$list.pol.df <- list()
    if(length(input$map_draw_all_features$features) == 0){return()}
    if(length(input$map_draw_all_features$features) >0){
      for(i in 1:length(input$map_draw_all_features$features)){
        values$list.pol.df[[i]] <- pol.coords(input$map_draw_all_features$features[[i]])
      }
    } 
    
  })
  
  observeEvent(input$ok, {
    if(length(values$list.pol.df) == 1){
      values$pol <- make.polygon(values$list.pol.df[[1]])
    }
    
    
    if(length(values$list.pol.df) > 1){
      
      values$pol <- bind(lapply(values$list.pol.df, make.polygon))
    }
    shape <- values$pol
    df <- data.frame(nome.poligono = paste("poligono", 1:length(values$list.pol.df)))
    
    # output
       shape <- SpatialPolygonsDataFrame(shape, df)
    
       writeOGR(shape, ".", "arquivo_poligono_Rhea", driver="ESRI Shapefile")
    
   
    
  })

  
}


shinyApp(ui,server)


```


